---
title: "Analysis Script"
author: "Shrishti Vaish"
date: "04/12/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Packages
```{r warning=FALSE, message=FALSE, results='hide'}
rm(list=ls())
library(ggplot2)
library(tidyverse)
```


# Reading dataset
```{r}
df <- read.csv("SampleSuperstore.csv")

str(df)
summary(df)
```

# Data preparation and Cleaning

Checking for abnormalities:
```{r}

#any null values?
is.null(df)

#any duplicacy?
dfnew <- df %>% distinct() ##yes, duplicates were removed
```

We see that there is an outlier in the Sales feature, an unusual hike. Let's replace it with the mean of sales.
```{r}
maxSales <- max(dfnew$Sales)
dfnew$Sales <- replace(dfnew$Sales, dfnew$Sales==maxSales,mean(dfnew$Sales))
```

# Removing country and Postal Codes feature
```{r}
dfnew <- dfnew %>% select(-c(Country, Postal.Code))
```


# Visualization
Let's analyze patterns in our cleaned data

### Sales vs Quantity
##### In the below graph, we see the following pattern that most of the sales have been triggered by the standard class of shipment mode.
```{r}
ggplot(data = dfnew, aes(x = Quantity, y = Sales, fill = Ship.Mode) )+ geom_bar(stat = "identity") 
```

### Sales vs Profit
And hence, obviously we see more profits/loss have been availed from the standard shipment class. But, there are not higher range profits seen this feature.
```{r}
ggplot(data = dfnew, aes(x = Sales, y = Profit, color = Ship.Mode)) + geom_point()
```


### Sales vs Discount
Let us see how Sales are affected if discounts are offered.
```{r}
ggplot() + geom_point(data = dfnew, aes(x = Discount, y = Sales, color = Ship.Mode)) 
```
*It is evident from the above graph that discounts attract more sales. But, discounts attract mostly the Standard Class shipment. Same day shipment mode receive the least disount offers.*



### Profits vs Discount
Let's see whether profits have been triggered if discounts have been redeemed.
```{r}
ggplot() + geom_bar(data = dfnew, aes(x = Discount, y = Profit, fill = Ship.Mode), stat = "identity") 
```

Yes, we see clearly, the more discounts have been offered and redeemed, the lesser profits the segments have achieved. 
Products with no discounts show high range of profits but as the discount range increases, we only see more and more loss with hardly any profit.


**Let us see if this is the case with other segments**
```{r}
ggplot() + geom_bar(data = dfnew, aes(x = Sub.Category, y = Profit, fill = Region), stat = "identity") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
**We see that more losses have been incurred by the *Binders* industry mainly in the Central region and *Machines* and * Tables * industry.**


### Now,
```{r}
ggplot() + geom_bar(data = dfnew, aes(x = Category, y = Sales, fill = Region), stat = "identity") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
**More Sales have been incurred by the technology category, then Furniture and  office supplies. Mostly sales have been made from the West and East regions**


```{r}
ggplot() + geom_bar(data = dfnew, aes(x = Category, y = Profit, fill = Region), stat = "identity") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

**The furniture category incurrs more losses than losses in the technology and Office Supplies category.**

Since, Sales also vary from low to high in this category so is are profits.

```{r}
ggplot() + geom_point(data = dfnew, aes(x = Sales, y = Profit, color = Category)) 
```

### We have now witnessed from the above graphs that the Sales to Profit ratio is same in every category, no matter how they are clubbed.



## Conclusion

#### **Recommended Solutions/ Key Insights**

*Same day shipment if receives more discounts can trigger sales/profits.*
*Discounts should be based on the Sales and should not increase a particular range otherwise unnecessary disounts with low sales can witness huge losses*
*Binders and Machines industry should be focused upon more so as to strengthen these weakened industry areas.*
*Office Supplies and the Furniture industries do not seem to boom in the Central Region.*


#                                                         THANK YOU!!
