---
title: "Analysis Script"
author: "Shrishti Vaish"
date: "04/12/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Packages
```{r warning=FALSE, message=FALSE, results='hide'}
rm(list=ls())
library(ggplot2)
library(tidyverse)
```


# Reading dataset
```{r}
df <- read.csv("SampleSuperstore.csv")

str(df)
summary(df)
```

# Data preparation and Cleaning

Checking for abnormalities:
```{r}

#any null values?
is.null(df)

#any duplicacy?
dfnew <- df %>% distinct() ##yes, duplicates were removed
```

We see that there is an outlier in the Sales feature, an unusual hike. Let's replace it with the mean of sales.
```{r}
maxSales <- max(dfnew$Sales)
dfnew$Sales <- replace(dfnew$Sales, dfnew$Sales==maxSales,mean(dfnew$Sales))
```

# Removing country and Postal Codes feature
```{r}
dfnew <- dfnew %>% select(-c(Country, Postal.Code))
```


# Visualization
Let's analyze patterns in our cleaned data

### Sales vs Quantity
##### In the below graph, we see the following pattern that most of the sales have been triggered by the standard class of shipment mode.
```{r}
ggplot() + geom_point(data = dfnew, aes(x = Quantity, y = Sales, color = Ship.Mode)) 
```

### Sales vs Profit
And hence, obviously we see more profits/loss have been availed from the standard shipment class. But, there are not higher range profits seen this feature.
```{r}
ggplot() + geom_point(data = dfnew, aes(x = Sales, y = Profit, color = Ship.Mode)) 
```


### Sales vs Discount
Let us see how Sales are affected if discounts are offered.
```{r}
ggplot() + geom_point(data = dfnew, aes(x = Discount, y = Sales, color = Ship.Mode)) 
```
*It is evident from the above graph that lesser discounts attract more sales. But, more discounts attract the Standard Class shipment. Same day shipment mode receive the least disount offers.*



### Profits vs Discount
Let's see if profits have been triggered if discounts have been redeemed.
```{r}
ggplot() + geom_point(data = dfnew, aes(x = Discount, y = Profit, color = Ship.Mode)) 
```

Yes, we see clearly, the more discounts have been offered and redeemed, the lesser profits the segments have achieved. 
Products with no discounts show high range of profits but as the discount range increases, we only see more and more loss with hardly any profit.


**Let us see if this is the case with other segments**
```{r}
ggplot() + geom_point(data = dfnew, aes(x = Sub.Category, y = Profit, color = Region)) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
**We see that more losses have been incurred by the *Binders* industry mainly in the Central region and *Machines* industry.**


### Now,
```{r}
ggplot() + geom_point(data = dfnew, aes(x = Category, y = Sales, color = Region)) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
**More Sales have been derived from the technology category, then office supplies and then Furniture.**


```{r}
ggplot() + geom_point(data = dfnew, aes(x = Category, y = Profit, color = Region)) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

**The office supplies category incurrs more loss in the central region, loss in the technology and Furniture category varies by region.**

Since, Sales also vary from low to high in this category so is are profits.

```{r}
ggplot() + geom_point(data = dfnew, aes(x = Sales, y = Profit, color = Category)) 
```

### We have now witnessed from the above graphs that the Sales to Profit ratio is same in every category, no matter how they are clubbed.



## Conclusion

#### **Recommended Solutions/ Key Insights**

*Same day shipment if receives more discounts can trigger sales/profits.*
*Discounts should be based on the Sales and should not increase a particular range otherwise unnecessary disounts woth low sales can witness huge losses*
*Binders and Machines industry should be focused upon more so as to strengthen these weakened areas.*
*Office Supplies in the Central Region should be focused upon more to make up losses. Preferred solutions could be discounts/variety or kind of supplies being offered.*


#                                                         THANK YOU!!
